Article 1:	Construct Validity and Correspondence of Google Trends

### 2022-02-22 paper1.Rmd
analysis prepped

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      # cache = TRUE,
                      fig.width = 7,
                      fig.asp = 0.8,
                      out.width = "80%",
                      fig.align="center"
                      # dev.args = list(png = list(type = "cairo"))
                      )

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
               modelsummary, showtext, thematic, kableExtra, scales,
               rmcorr)

my_palette = c('#56b4e9','#999999','#E69F00','#009E73','#CC79A7','#0072B2','#D55E00','#E69F00')
my_palette  <- c(MetBrewer::met.brewer(name = 'Cross', type = 'discrete'), '#555F61')

## Automatically use showtext to render text
font_add_google("Lora", "lora")
showtext_auto()

theme_diss <- function(base_size = 14) {
  theme_minimal(base_size = base_size) %+replace%
    theme(
      # Figure assembly
      plot.title = element_text(family="lora",
                                size = rel(1), 
                                margin = margin(0,0,5,0), 
                                hjust = 0),
      plot.title.position = "plot",
      plot.subtitle = element_text(family="lora",
                                   size = rel(0.85)),
      plot.caption = element_text(family="lora",
                                  size = rel(0.70),
                                  hjust = 1),
      # Graphical Zones
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Axes
      axis.title = element_text(family="lora", 
                                size = rel(0.85)),
      axis.text = element_text(family="lora", 
                               size = rel(0.70)),
      axis.line = element_line(color = "black", 
                               arrow = arrow(length = unit(0.3, "lines"), 
                                             type = "closed")),
      # Legend
      legend.title = element_text(family="lora",
                                  size = rel(0.85)),
      legend.text = element_text(family="lora", 
                                 size = rel(0.70)),
      legend.key = element_rect(fill = "transparent", 
                                colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", 
                                       colour = NA),
      # Facetting 
      strip.background = element_rect(fill = "#17252D",
                                      color = "#17252D"),
      strip.text = element_text(family="lora",
                                size = rel(0.85), 
                                color = "white", 
                                margin = margin(5,0,5,0))
    )
}

theme_set(theme_diss())

```
```{r data}
vacc_hes <- read_rds(here('data', 'cleaned_data', 'vacc_hes.rds'))
mask <- read_rds(here('data', 'cleaned_data', 'mask.rds'))
covid <- read_rds(here('data', 'cleaned_data', 'covid.rds'))
suicide <- read_rds(here('data', 'cleaned_data', 'suicide.rds'))
pres_2016 <- read_rds(here('data', 'cleaned_data', 'pres_2016.rds'))
pres_2020 <- read_rds(here('data', 'cleaned_data', 'pres_2020.rds'))
```

@@

@@

I first use U.S. Covid-19 rates to validate health and disease related topics. I
retrieve U.S. county-level Covid-19 rates from by @covid_data, who compile this
data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test
[@gu22; @cdc20a] However, it is the best measure we have of actual case rates.
Case Rate is measured as number of cases per 100,000 population. Observations
vary from a minimum of 0 to a maximum of `r max(covid$covid_rate))` for each 
Monday from `r glue("{format( min(covid$date), '%B %d, %Y')} through {format(max(covid$date), '%B %d, %Y')}")`.
There are `r nrow(covid)` cases across `r nrow(count(covid, fips))` 
counties and `r nrow(count(covid, date))` dates. Missing data were interpolated 
using `zoo::na.approx()` [@zoo].

@@

In addition, I use data on political opinions from the the American National
Election Survey 2020 Time-Series Study [@anes_data]. This data is paired with
restricted data provided by ICPSR, the Inter-university Consortium for Political
and Social Research, that contains the geo-ids of the `r 5,441` survey respondents.
The study interviewed respondents in a pre-election survey that was conducted
between August 18, 2020 and the day of the US Presidential election day,
November 3, 2020.

@@

To address longitudinal correlations, I employ Repeated Measures Correlation
[@bland1995] using the `rmcorr` package in R [@bakdash2017]. Repeated Measures
Correlation is useful for determining the within-individual association for
paired measures across time and individuals.

I test both the raw trends, as well a combination of trends created
through factor analysis as a method of dimensionality reduction.

As an additional test of correlation, I employ multiple linear
regression to identify the strength of relationships across locales: I
include city-data like county population size, internet usage rates, and
Z to attempt to disentangle why some individual cases may be better predicted by
Google Trends while others may not.

visualizations made with [@wickham11; @wickham_etal]

@@

@@

```{r}
covid_corr <- rmcorr::rmcorr(fips, measure1 = covid_rate, measure2 = covid_19, dataset = covid)

covid_reg <- lm(covid_rate ~ covid_19 + smell_loss + taste_loss, data = covid)

```{r}
suicide_corr <- rmcorr::rmcorr(fips, measure1 = death_rate, measure2 = suicide, dataset = suicide)

suicide_reg <- lm(death_rate ~ suicide + depression + suicide_hotline, data = suicide)
summary(suicide_reg)

library(nlme)

suicide <- suicide %>% 
  drop_na()
suicide_lme <- lme(fixed = death_rate ~ suicide + depression + suicide_hotline,
             random = ~ 1 | fips,
             data = suicide)
summary(suicide_lme)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      cache = TRUE,
                      fig.width = 7,
                      fig.asp = 0.8,
                      out.width = "80%",
                      fig.align="center"
                      # dev.args = list(png = list(type = "cairo"))
                      )

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
               modelsummary, showtext, thematic, kableExtra, scales, nlme)

my_palette  <- c(MetBrewer::met.brewer(name = 'Cross', type = 'discrete'), '#555F61')

stars <- function(p.value){
  unclass(symnum(p.value, 
                 corr = FALSE, 
                 na = FALSE, 
                 cutpoints = c(0, 0.001, 0.01, 0.05, 1), 
                 symbols = c("***", "**", "*", " ")))
}

```
```{r data}
vacc_hes <- read_rds(here('data', 'cleaned_data', 'vacc_hes.rds'))
mask <- read_rds(here('data', 'cleaned_data', 'mask.rds')) %>%  ungroup()
covid <- read_rds(here('data', 'cleaned_data', 'covid.rds'))
suicide <- read_rds(here('data', 'cleaned_data', 'suicide.rds'))
pres_2016 <- read_rds(here('data', 'cleaned_data', 'pres_2016.rds'))
pres_2020 <- read_rds(here('data', 'cleaned_data', 'pres_2020.rds'))

@@

<!-- TODO: VARIABLE SCALE -->

@@

I first use U.S. Covid-19 rates to validate health and disease related topics. I
retrieve U.S. county-level Covid-19 rates from by @covid_data, who compile this
data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test
[@gu22; @cdc20a] However, it is the best measure we have of actual case rates.
Case Rate is measured as number of cases per 100,000 population. Observations
vary from a minimum of 0 to a maximum of `r max(covid$covid_rate)` for each 
Monday from `r glue("{format( min(covid$date), '%B %d, %Y')} through {format(max(covid$date), '%B %d, %Y')}")`.
There are `r nrow(covid)` cases across `r nrow(count(covid, fips))` 
counties and `r nrow(count(covid, date))` dates. Missing data were interpolated 
using `zoo::na.approx()` [@zoo].

<!-- TODO: VARIABLE SCALE -->

@@

<!-- TODO: VARIABLE SCALE -->

In addition, I use data on political opinions from the the American National
Election Survey 2020 Time-Series Study [@anes_data]. This data is paired with
restricted data provided by ICPSR, the Inter-university Consortium for Political
and Social Research, that contains the geo-ids of the `r scales::label_comma()(5441)`
survey respondents. The study interviewed respondents in a pre-election survey
that was conducted between August 18, 2020 and the day of the US Presidential
election day, November 3, 2020.

<!-- TODO: VARIABLE SCALE -->

### Other

In addition to specific outcomes of interest, I also gathered various county
controls to investigate possible variable confounding. The first Seven of these
variables come from the 2010-2019 5-year American Community Surveys [@acs2019;
@acs2018; @acs2017; @acs2016; @acs2015; ; @acs2014; @acs2013; @acs2012;
@acs2011; @acs2010]. These data include total population, population density,
unemployment rate for those 16 and over, median county income, average commute
time, percent of households living under the poverty line, and percent above 65
years old. In addition, some models employ the U.S. Current Population Survey &
American Community Survey Geographic Estimates of Internet Use, 1997-2018
[@internet_use] to estimate households with broadband internet subscriptions.
This final variable is an attempt to capture the latent propensity to use the
internet for information search.

<!-- ACS 5 year estimates -->
<!-- a00001 total population -->
<!-- a00002 population density -->
<!-- a17005 unemployment rate 16+ -->
<!-- a14006 median income -->
<!-- a09003 average commute time -->
<!-- poverty percent -->
<!-- 01001B 65 plus -->

@@

To address longitudinal correlations, I employ Repeated Measures Correlation
using the `rmcorr` package in R [@bland1995; @bakdash2017]. Repeated Measures
Correlation is useful for determining the within-county association for paired
measures across time and counties.

As an additional test of the relationships, I employ multiple linear regression
to identify the strength of relationships across locales: I include city-data
like county population size, broadband rates, and median income to attempt to
disentangle possible confounders of the relationship between Google search
Trends and verified indicators. Identifying these possible confounded
relationships will help to explain why some articles find relationships between
the trends and outcomes while others did not. For linear regression models, I
normalize independent variables, i.e.variables have been centered and scaled to
have a mean of 0 and standard deviation 1.

@@

```{r vacc_hes_analysis1}
tribble(
  ~'measure',~'covid_conspiracy', ~'covid_19_vaccine', ~'coronavirus', ~'covid_19', 
  "vacc_hes, Pearson's R Correlation",
  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_conspiracy, use = "complete.obs"),
  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19_vaccine, use = "complete.obs"),
  cor(vacc_hes$vacc_hesitant, vacc_hes$coronavirus, use = "complete.obs"),
  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19, use = "complete.obs")
)  %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r vacc_hes_analysis2}
vacc_hes <- vacc_hes %>% 
  select(-c(DMA_google, Geo_QName)) %>% 
  mutate(across(covid_conspiracy:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))

vacc_hes_1  <- lm(vacc_hesitant  ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income + broadband,
                  data = vacc_hes)
vacc_hes_2 <- lm(vacc_hesitant  ~  covid_19_vaccine +     
                   coronavirus +covid_19,
                 data = vacc_hes)
vacc_hes_2b <- lm(vacc_hesitant  ~ covid_conspiracy + covid_19_vaccine +
                    coronavirus +covid_19,
                  data = vacc_hes)
vacc_hes_3  <- lm(vacc_hesitant  ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income + broadband + 
                    covid_19_vaccine +
                    coronavirus +covid_19,
                   data = vacc_hes)

modelsummary(list(vacc_hes_1, vacc_hes_2, vacc_hes_2b,vacc_hes_3), 
             # title = "Linear Regression Results for Vaccine Hesitancy",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE'
             ) %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

pearson correlations
rsquared
coefficients
conclusion

```{r mask_analysis1}
tribble(
  ~'measure',~'face_mask', ~'mask', ~'cloth_face_mask',  
  "Mask Rare, Pearson's R Correlation",
  cor(mask$mask_rare, mask$face_mask, use = "complete.obs"),
  cor(mask$mask_rare, mask$mask, use = "complete.obs"),
  cor(mask$mask_rare, mask$cloth_face_mask, use = "complete.obs")
)  %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r mask_analysis2}
mask <- mask %>% 
  select(-c(DMA_google, Geo_QName)) %>% 
  mutate(across(face_mask:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))

mask_1  <- lm(mask_rare  ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income + broadband,
                  data = mask)
mask_2 <- lm(mask_rare  ~  face_mask + mask + cloth_face_mask,
                 data = mask)
mask_3  <- lm(mask_rare  ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income + broadband + 
                    face_mask + mask + cloth_face_mask,
                   data = mask)

modelsummary(list(mask_1, mask_2, mask_3), 
             # title = "Linear Regression Results for Rare Mask Usage",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

```
pearson correlations
rsquared
coefficients
conclusion

@@

```{r covid_analysis1}
covid_corrs <- read_rds(here('data', 'from_hpc', 'covid_corrs.rds'))
# covid_corrs[1,1] <- "Covid Rate, Pearson's R Correlation"
# write_rds(covid_corrs, here('data', 'from_hpc', 'covid_corrs.rds'))

covid_corrs %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r covid_analysis2}
covid <- covid %>% 
  select(-c(dma_google, Geo_QName, county, state)) %>% 
  mutate(across(covid_19:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1])) %>% 
  left_join(covid %>%
              group_by(fips) %>%
              summarize(covid_rate_fips_mean = mean(covid_rate, na.rm = TRUE)),
            by = "fips") %>% 
  drop_na(covid_rate)

covid_1  <- lme(covid_rate  ~ 
                  total_pop + pop_density + unemployment_rate + 
                  over_65 + poverty_rate + median_income + broadband +
                  covid_rate_fips_mean + date,
                random = ~ 1 | fips, na.action=na.omit,data = covid)
covid_2 <- lme(covid_rate  ~  
                 covid_19 + smell_loss + taste_loss + covid_rate_fips_mean  + 
                 date,
               random = ~ 1 | fips, na.action=na.omit, data = covid)
covid_3  <- lme(covid_rate  ~ 
                  total_pop + pop_density + unemployment_rate + 
                  over_65 + poverty_rate + median_income + broadband + 
                  covid_19 + smell_loss + taste_loss + covid_rate_fips_mean  +
                  date,
                random = ~ 1 | fips, na.action=na.omit, data = covid)

modelsummary(list(covid_1, covid_2, covid_3), 
             # title = "Hierarchical Model for Covid Case Rates",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Random intercept per county'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

# TODO Drop SD intercept and observations,

```
pearson correlations
rmcorr
rsquared
coefficients
conclusion

```{r suicide_analysis1}
suicide_corrs <- read_rds(here('data', 'from_hpc', 'suicide_corrs.rds'))

# suicide_corrs[1,1] <- "Death by Suicide Rate, Pearson's R Correlation"
# suicide_corrs[2,1] <- "Death by Suicide Rate, rmcorr"
# 
# write_rds(suicide_corrs, here('data', 'from_hpc', 'suicide_corrs.rds'))

suicide_corrs %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r suicide_analysis2}
suicide <- suicide %>% 
  select(-c(dma_google, Geo_QName, county, population, deaths)) %>% 
  mutate(across(suicide:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1])) %>% 
  left_join(suicide %>%
              group_by(fips) %>%
              summarize(death_rate_fips_mean = mean(death_rate , na.rm = TRUE)),
            by = "fips") %>% 
  drop_na(death_rate )

suicide_1  <- lme(death_rate   ~ 
                  total_pop + pop_density + unemployment_rate + 
                  over_65 + poverty_rate + median_income + broadband +
                  death_rate_fips_mean + year,
                random = ~ 1 | fips, na.action=na.omit,data = suicide)
suicide_2 <- lme(death_rate   ~  
                 suicide + depression + suicide_hotline + death_rate_fips_mean  + 
                 year,
               random = ~ 1 | fips, na.action=na.omit, data = suicide)
suicide_3  <- lme(death_rate   ~ 
                  total_pop + pop_density + unemployment_rate + 
                  over_65 + poverty_rate + median_income + broadband + 
                  suicide + depression + suicide_hotline + death_rate_fips_mean  +
                  year,
                random = ~ 1 | fips, na.action=na.omit, data = suicide)

modelsummary(list(suicide_1, suicide_2, suicide_3), 
             # title = "Hierarchical Model for Suicide Rates",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Random intercept per county'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

# TODO Drop SD intercept and observations,
# TODO why is the r2 so high? death_rate_fips_mean?
```
pearson correlations
rmcorr
rsquared
coefficients
conclusion

@@

```{r pres_2016_analysis1}
tribble(
  ~'measure',~'Searches for Hilary Clinton', ~ 'Searches for Donald Trump',
  "Votes for Clinton, Pearson's R Correlation",
  cor(pres_2016$clinton_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),
  cor(pres_2016$clinton_p, pres_2016$`Donald Trump`, use = "complete.obs"),

  "Votes for Trump, Pearson's R Correlation",
  cor(pres_2016$trump_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),
  cor(pres_2016$trump_p, pres_2016$`Donald Trump`, use = "complete.obs"),
)  %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r pres_2016_analysis2}
pres_2016 <- pres_2016 %>% 
  select(-c(Geo_QName, dma)) %>% 
  mutate(across(c(`Hilary Clinton`,`Donald Trump`:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))

vacc_hes_1a  <- lm(clinton_p   ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income,
                  data = pres_2016)
vacc_hes_2a <- lm(clinton_p   ~  `Donald Trump` + `Hilary Clinton`,
                 data = pres_2016)

vacc_hes_3a  <- lm(clinton_p   ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income + 
                     `Donald Trump` + `Hilary Clinton`,
                   data = pres_2016)

vacc_hes_1b  <- lm(trump_p    ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income,
                  data = pres_2016)
vacc_hes_2b <- lm(trump_p    ~  `Donald Trump` + `Hilary Clinton`,
                 data = pres_2016)

vacc_hes_3b  <- lm(trump_p    ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income + 
                     `Donald Trump` + `Hilary Clinton`,
                   data = pres_2016)

modelsummary(list(vacc_hes_1a, vacc_hes_2a,vacc_hes_3a 
                  # ,vacc_hes_1b, vacc_hes_2b,vacc_hes_3b
                  ), 
             # title = "Linear Regression Results for 2016 Presidential Election Results (Hilary Clinton Shown)",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Results predicting Donald J. Trump percentage largely equivalent and available upon request.'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE'
             ) %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

```
pearson correlations
rsquared
coefficients
conclusion

```{r pres_2020_analysis1}
tribble(
  ~'measure',~'Searches for Joe Biden', ~ 'Searches for Donald Trump',
  "Votes for Biden, Pearson's R Correlation",
  cor(pres_2020$biden_p, pres_2020$`Joe Biden`, use = "complete.obs"),
  cor(pres_2020$biden_p, pres_2020$`Donald Trump`, use = "complete.obs"),

  "Votes for Trump, Pearson's R Correlation",
  cor(pres_2020$trump_p, pres_2020$`Joe Biden`, use = "complete.obs"),
  cor(pres_2020$trump_p, pres_2020$`Donald Trump`, use = "complete.obs"),
)  %>% 
  kbl(digits=4) %>%
  #overall styling
  kable_styling(latex_options = c( "hold_position"), full_width = T)
```

```{r pres_2020_analysis2}
pres_2020 <- pres_2020 %>% 
  select(-c(Geo_QName, dma)) %>% 
  mutate(across(c(`Joe Biden`,`Donald Trump`:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))

vacc_hes_1a  <- lm(biden_p   ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income,
                  data = pres_2020)
vacc_hes_2a <- lm(biden_p   ~  `Donald Trump` + `Joe Biden`,
                 data = pres_2020)

vacc_hes_3a  <- lm(biden_p   ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income + 
                     `Donald Trump` + `Joe Biden`,
                   data = pres_2020)

vacc_hes_1b  <- lm(trump_p    ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income,
                  data = pres_2020)
vacc_hes_2b <- lm(trump_p    ~  `Donald Trump` + `Joe Biden`,
                 data = pres_2020)

vacc_hes_3b  <- lm(trump_p    ~ 
                    total_pop + pop_density + unemployment_rate + 
                    over_65 + poverty_rate + median_income + 
                     `Donald Trump` + `Joe Biden`,
                   data = pres_2020)

modelsummary(list(vacc_hes_1a, vacc_hes_2a,vacc_hes_3a 
                  # ,vacc_hes_1b, vacc_hes_2b,vacc_hes_3b
                  ), 
             # title = "Linear Regression Results for 2020 Presidential Election Results (Joe Biden Shown)",
             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
                      'Results predicting Donald J. Trump percentage largely equivalent and available upon request.'),
             estimate = "{estimate}{stars}",
             gof_omit = 'AIC|BIC|ICC|RMSE'
             ) %>%
  kable_styling(latex_options = c("hold_position", 'condensed'),
                font_size = 8)

```
pearson correlations
rsquared
coefficients
conclusion
